## Functions and Conditionals

### Conditionals

The basic syntax for an if statement goes like this:

```{r}
if (logical statement) {
  do something
} else {
  do something else
}
```

The logical statements should boil down to a boolean; for example:

```{r}

```

We can also add else if statements in the middle if we need more options.

```{r}

```

Neat! We can also nest conditionals just like we do in Python.

```{r}

    
```

Neat! Now, let's look at another core part of R programming - Loops!

### Loops

```{r}

```

We can also do nifty stuff with our vectors, such as apply changes to specific indices of our data.

```{r}

```

We can loop over more than just lists:

```{r}

```

Like Python, we have while loops in R:

```{r}

```

## Functions

When should we use functions?

```{r}
our_function <- function(optional_params){
  # do some stuff
}
```

An example:

```{r}

```

This is all cool.. but it didn't do anything. We need to call the function!

```{r}

```

Notice that in the background here, we are looping over each item in the array, but we never write a for loop! Keep this in mind, since when you pass in a large data set, the changes made by functions aren't quite immediate - the computer does have to go over each item in your data set, and change them one at a time.

A shortcut of sorts is to use the `apply()` function, which operates very similarly to Python's `map()`. Note that `apply` syntax goes as follows: `apply(X, MARGIN, FUN)` where X is the data set to use, MARGIN is specification for rows or columns, and FUN is the function to apply.

```{r}

```

It is common to use `mean`, `median`, `sum`, `min`, or `max` with `apply`, but we can also use our user-defined functions as well. Note that apply() only works with matrices.

```{r}

```

### Homework

1.  Do 5 CodeWars problems in R. Share your solutions here:

    ```{r}
    # Leap year
    is_leap_year <- function(year) {
      if (year %% 4 == 0 & year %% 100 != 0) {
        return (TRUE)
      } else if (year %% 400 == 0) {
        return (TRUE)
      } else {
        return (FALSE)
      }
    }
    # Smash Words
    smash <- function(words){
      sentence <- ''
      for (x in words) {
        sentence <- paste(sentence, x)
        
      }
      sentence <- trimws(sentence)
      print(sentence)
    }
    sum_array <- function(a){
      total = sum(a)
      return(total)
    }
    digitize <- function(n){
      n_chars <- as.character(n)
      numbers <- strsplit(n_chars, "")[[1]]
      list <- rev(as.numeric(numbers))
      print(list)
      return(list)
    }
    invert <- function(vec){
      print(vec)
      for (i in seq_along(vec)) {
        vec[i] <- vec[i]*-1
      }
      print(vec)
    }
    ```

2.  Create a function that checks an input of type `int` and returns fizz if the number is a multiple of 3, buzz if the number is a multiple of 5, and fizzbuzz if the number is a multiple of 3 and 5.

    ```{r}
number = 20L
value = class(number)
value
if (value == "integer" & number %% 3 == 0) {
  if (number %% 5 == 0){
      print("fizzbuzz")   
  } else {
    print("fizz")
  }

} else if (number %% 5 == 0) {
    print("buzz")
  
}
    ```

3.  **Mario Challenge:** In the classic Super Mario games, Mario ends each level by ascending a flight of stairs and leaping off the top to arrive at the castle at the end. (See [here](https://youtu.be/-avspZlbOWU?t=55) for details). We can imagine that each of the bricks of the stairs is a character X. Create a function that prints out a set of stairs. For example:

    If the function is called marioStairs() and we pass in the value 4, we would expect to see stairs with a length of 4 and a height of 4:

    X

    XX

    XXX

    XXXX

    ```{r}
    # You may feel more comfortable figuring this out in Python first, then translating into R later.
    ````
